Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2021-01-04 awipev-CO2.Rmd
pco2_fb at in situ temp

```{r read data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2 = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
```

@@

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```
```{r read and prepare nutrient data, echo=FALSE, warning=TRUE, message=FALSE}
# File "Ferrybox nutrients 2014-2018.xlsx" provided by 
# Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
# nutrients in umol/l
nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
                           skip =1) %>% 
  drop_na(date) %>% 
  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00"))) %>% # assuming sampling time 12:00
  dplyr::filter(datetime > as.POSIXct("2015-07-09"))
# The nearest times
time_index <- unique(d_all$datetime)
# nuts$closest <- time_index[
#   FNN::knnx.index(time_index, # The values to be queried (big df)
#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
#                   k = 1)] # The number of closest values to return
nuts <- nuts %>% 
  dplyr::mutate(closest = time_index[
  FNN::knnx.index(time_index, # The values to be queried (big df)
                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
                  k = 1)]) %>%  # The number of closest values to return
  dplyr::select(-date, -datetime) %>% 
  dplyr::rename(no3no2 = `no3+no2`)
# cleanup and convert in umol/kg
d_all <- left_join(d_all, nuts, by = c("datetime" = "closest")) #%>% 
  #dplyr::select(-closest_datetime)
d_all <- d_all %>% 
  dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
                po4 = po4 / (density_fb/1000),
                nh4 = nh4 / (density_fb/1000),
                no3no2 = no3no2 / (density_fb/1000),
                no3 = no3 / (density_fb/1000),
                si = si / (density_fb/1000)
  )
```

@@

## *p*CO~2~
The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015. It was deployed in the FerryBox with other sensors since July 2015, the 20th. A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem. Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_fb , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = monthd))+
   geom_text(aes(color = factor(monthd)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc_fb",
    label = "pco2_calc_fb",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    pco2_corr = case_when(
      date > as.Date("2016-04-01") &
        date <  as.Date("2017-02-05") & pco2_corr > 400 ~ NA_real_,
      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2017-08-01") &
        date <  as.Date("2017-09-30") & pco2_corr > 300 ~ NA_real_,
      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
      TRUE ~ pco2_corr
    )
  )
```

@@

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
pander(const)
```
### Using all values pCO2 and at_calc
```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
d_ls <- d_all %>% 
  drop_na(pco2_corr, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    d_ls$pco2_corr,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    d_ls$pco2_corr,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s)
d_ls <- bind_cols(d_ls, diff_ls)

@@

##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
d_all <- d_all %>%
  dplyr::mutate(delta_pco2 = pco2_corr - pco2_air, # ppm
                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
                k = k600 * (Sc/600)^-0.5, #cm/h
                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
                )

@@

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
  dplyr::rename(pressure = pressure_insitu_ctd,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                s_mix = sal_mix,
                t_11m = temp_insitu_11m,
                t_insitu = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_sf = temp_sf, 
                t_dur = temp_dur, 
                at = at, 
                at_calc =at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_corr,
                pco2_calc = pco2_calc_fb,
                pH_sf = pHint_tot_sf,
                ph_dur = ph_dur_corr,
                ph_calc = phcalc_fb
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
# t_11m = temperature in situ at 11 m
# t_insitu = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler), °C
# t_dur = temperature Durafet (FerryBox)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
# pco2 = pCO2 in Ferrybox
# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
# pH_sf = pH SeaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
# ph_calc = pH at fb temp calculated from CT and AT samples collected at the FerryBox
```
## Maintenance
<div style="text-align: justify">

>>>>

```{r read observatory data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <-
  readRDS(file = paste0(
    path,
    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
  ))
d_hour <- d_hour %>%
  dplyr::rename(
    pco2_fb = pco2_corr_filtered,
    temp_dur = temp_dur_filtered,
    pco2_raw = pco2_raw_filtered,
    sal_fb = sal_fb_filtered,
    temp_insitu_11m = temp_insitu_11m_filtered,
    temp_fb = temp_fb_filtered,
    ph_dur = ph_dur_filtered
  ) %>% 
  arrange(datetime)
d_all <- as_tibble(d_hour) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 9, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
```

@@

# create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_fb <- NA
discrete_is_na$pco2_calc_fb <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)
```
```{r read and prepare nutrient data, echo=FALSE, warning=TRUE, message=FALSE}
# File "Ferrybox nutrients 2014-2018.xlsx" provided by 
# Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
# nutrients in umol/l
nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
                           skip =1) %>% 
  drop_na(date) %>% 
  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00")),
                ) %>% # assuming sampling time 12:00
  dplyr::filter(datetime > as.POSIXct("2015-07-09"))
# The nearest times
time_index <- unique(d_all$datetime)
# nuts$closest <- time_index[
#   FNN::knnx.index(time_index, # The values to be queried (big df)
#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
#                   k = 1)] # The number of closest values to return
nuts <- nuts %>% 
  dplyr::mutate(closest = time_index[
  FNN::knnx.index(time_index, # The values to be queried (big df)
                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
                  k = 1)]) %>%  # The number of closest values to return
  dplyr::select(-date, -datetime) %>% 
  dplyr::rename(NO3NO2 = `NO3+NO2`)
# cleanup and convert in umol/kg
d_all <- left_join(d_all, nuts, by = c("datetime" = "closest")) #%>% 
  #dplyr::select(-closest_datetime)
d_all <- d_all %>% 
  dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
                po4 = PO4 / (density_fb/1000),
                nh4 = NH4 / (density_fb/1000),
                no3no2 = NO3NO2 / (density_fb/1000),
                no3 = NO3 / (density_fb/1000),
                si = Si / (density_fb/1000)
  )
```

@@

## *p*CO~2~ and *f*CO~2~
The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015. It was deployed in the FerryBox with other sensors since July 2015, the 20th. A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem. Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):

@@

```{r pco2 to fco2, echo=FALSE, warning=FALSE, message=FALSE}
d_all <- d_all %>%
  dplyr::mutate(
    fco2_fb = seacarb::p2fCO2(
      pCO2 = pco2_fb,
      T = temp_fb,
      Patm = 1,
      P = 0),
    fco2_fb_insi_temp = seacarb::fCO2insi(
      fCO2lab = fco2_fb,
      Tlab = temp_fb,
      SST = temp_insitu_11m),
    .after = pco2_fb
)
```

We first calculate fCO2 from pCO2 and then express fCO2 at in situ temperature. Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes. I therefroe use the in situ temperature at 11 m and we will need to speculate on stratitication.

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_fb ~ pco2_calc_fb , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_fb, label = monthd))+
   geom_text(aes(color = factor(monthd)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_fb_pco2_corr_text
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_fb)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_fb",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc_fb",
    label = "pco2_calc_fb",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    pco2_fb = case_when(
      date > as.Date("2016-04-01") &
        date <  as.Date("2017-02-05") & pco2_fb > 400 ~ NA_real_,
      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
      date > as.Date("2017-08-01") &
        date <  as.Date("2017-09-30") & pco2_fb > 300 ~ NA_real_,
      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
      TRUE ~ pco2_fb
    )
  )
```

@@

# impacts using AT-DIC pair
carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                 Pt = 0, Sit = 0,
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                Pt = 0, Sit = 0, 
                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
diff_ls_2 <- carb_l_2 - carb_s_2
const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
                S = mean_sal,
                T = mean_temp,
                DIC = DIC * 1e6
                ) %>% 
  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
pander(const)
```
### Using all values pCO2 and at_calc
```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis
d_ls <- d_all %>% 
  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
carb_l <-
  carb(
    24,
    d_ls$pco2_fb,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "l",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
carb_s <-
  carb(
    24,
    d_ls$pco2_fb,
    d_ls$at_calc * 1e-6,
    S = d_ls$sal_fb,
    T = d_ls$temp_fb,
    P = 0,
    Pt = 0,
    Sit = 0,
    k1k2 = "s20",
    kf = "dg",
    ks = "d",
    pHscale = "T",
    b = "u74"
  )
diff_ls <- as_tibble(carb_l - carb_s)
d_ls <- bind_cols(d_ls, diff_ls)

@@

##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
d_all <- d_all %>%
  dplyr::mutate(delta_pco2 = pco2_fb - pco2_air, # ppm
                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
                k = k600 * (Sc/600)^-0.5, #cm/h
                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
                )

@@

pangaea <- as_tibble(d_all) %>% 
  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
  dplyr::rename(pressure = pressure_insitu_ctd,
                s_insitu = sal_insitu_ctd,
                s_fb = sal_fb, 
                s_mix = sal_mix,
                t_11m = temp_insitu_11m,
                t_insitu = temp_insitu_ctd, 
                t_fb = temp_fb, 
                t_sf = temp_sf, 
                t_dur = temp_dur, 
                at = at, 
                at_calc =at_calc,
                ct = ct, 
                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
                ph_s_dur_t_fb = ph_s_dur_temp_fb,
                pco2 = pco2_fb,
                pco2_calc = pco2_calc_fb,
                pH_sf = pHint_tot_sf,
                ph_dur = ph_dur_corr,
                ph_calc = phcalc_fb
                )
saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
# Metadata Pangaea
# pressure = pressure in situ (profiler)
# s_insitu = salinity in situ (profiler)
# s_fb = salinity in FerryBox 
# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
# t_11m = temperature in situ at 11 m
# t_insitu = temperature in situ (profiler), 
# t_fb = temperature in FerryBox 
# t_sf = temperature SeaFET (profiler), °C
# t_dur = temperature Durafet (FerryBox)
# at = total alkalinity, discrete measurements (FerryBox)
# at_calc = total alkalinity, calculated from salinity
# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
# pco2 = pCO2 in Ferrybox
# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
# pH_sf = pH SeaFET at in situ temperature (profiler)
# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
# ph_calc = pH at fb temp calculated from CT and AT samples collected at the FerryBox
```
## Maintenance
<div style="text-align: justify">
